---
title: "BSMM-lab-3"
subtitle: "BSMM 8740 Fall 2023"
author: "Turusha Ghimire"
date: "1st October 2023"
format: html
editor: visual
self-contained: true
---

## Setup

Load packages and data:

```{r load-pkg-data}
#| message: false
#install.packages("tidyverse")
#install.packages("gt")          
#install.packages("gtExtras")     
#install.packages("DataExplorer")
#install.packages("tidymodels")
#install.packages("gt")
boston_cocktails <- readr::read_csv('data/boston_cocktails.csv')
```

```{r}
install.packages("skimr")
install.packages("janitor")
```

## Exercises

### Exercise 1

The median measure amount across across all cocktails is \_\_\_.

```{r}
library(magrittr)    
library(tidyverse)
boston_cocktails %>%
  skimr::skim()
DataExplorer::introduce(boston_cocktails)
```

```{r}
boston_cocktails %>%
  summary()
```

### Exercise 2

The **Leap Frog Highball** contains \_\_\_ of gin \
**Answer : 2**

```{r}
selected_col <- dplyr::select(boston_cocktails, name, category, ingredient, measure_number)

pivoted_data <-selected_col %>%
  pivot_wider(names_from = ingredient, values_from = measure_number, values_fill = 0)
pivoted_data <- janitor::clean_names(pivoted_data)
pivoted_data
```

```{r}
cleaned_data <- pivoted_data %>%
  drop_na()
new_ds <- cleaned_data
new_ds
```

```{r}
leap_frog_highball <- new_ds %>%
  filter(name == "Leap Frog Highball") %>%
  select(gin)

# Print the amount of gin in the cocktail
print(leap_frog_highball)
```

### Exercise 3

\_\_\_ predictor variables are prepped by the recipe.

```{r}
#install.packages("recipe")
```

```{r}
#library(recipes)
# Create a recipe object
#recipe_obj <- recipe_obj %>%
 # recipe::update_role(name,categor='id')
#summary(recipe_obj)

  
 
```

### Exercise 4

On average the most used ingredient in the Boston Cocktails dataset is \_\_\_\_.

### Exercise 5

Describe describe the drinks represented by PC1?

### Exercise 6

The characteristic alcoholic beverage of each of the first 4 principle components is \_\_\_.

### Exercise 7

How would you interpret the results of a PCA analysis for a client?
